---
title: "Run and plot AMPS calibration"
author: "Hem Nalini Morzaria-Luna"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
#turn off scientific notation so numbers with decimals are printed
options(scipen = 999)

#only packages that are needed as loaded, functions from other packages are called directly as dplyr::filter
# List of packages for session
.packages = c("parallel","doSNOW")
#install.packages(.packages, dependencies = TRUE)
# Load packages into session 
lapply(.packages, require, character.only=TRUE)


devtools::load_all()
```


Check these entries before running, specifies runs, paths and plots to generate
```{r set run, include=FALSE}

flagnoclusters = 0 #flag to run on multiple cores, 1 to run on all cores except one, 0 to run on all cores, can help access Rstudio while Atlantis runs are going

#Check before running
#Name of sheet used in Google sheet calibration log
sheet.name = "calibration_log_HML"

#runs that will be modified, based on run_no in the spreadsheet
runs.modify <- 1:8

#specify email used to access the Google sheet
myemail <- "hmorzarialuna@gmail.com"#"myemail@gmail.com"

#directory with base run
base.dir <- "/home/atlantis/psatlantismodel/Atlantis_mv1_base_2024_5yrs_V2"
#directory where to store runs
run.dir <- "/nfsdata/ampscalibration"
#name of biology prm
prm.name <- "AMPSbioparam_mv1_2024_V4.prm"

sh.file <- "amps_cal.sh" #original sh file

startyear <- 2011 #model start year
runtime <- 3650 #length of runs in days
outputfrequency <- 73 #output frequency in days
#set maxtimestep to the maximum number of days you want to plot in comparison files
maxtimestep <- 3650
this.nc <- "AMPS_2024.nc"
this.output.nc <- "AMPS_OUT.nc" #name of output nc file

#options for diet plots
atlantis.bgm <- here::here("data-raw","PugetSound_89b_070116.bgm")
outdietfile <- "AMPS_OUTDietCheck.txt"

threshold <- 0.2 #threshold for diet plots, will only show groups that correspond to this and higher proportion of the diet
starttimediet <- 0 #minimum timestep selected for diet plots, it will show data from this point
endtimediet <- 3650 #maximum timestep selected for diet plots, it will show data up this point
#End check these entries before running

#plots to run, if these flags are turned off, this RMD will only create run folders, run them and gather output
runbaseplots <- 1 #baseplots are Biomass, ResN, StrN, Numbers, Weight-at-age for individual runs
runcomparebiomass <- 1 #compare biomass plots
runguildbiomass <- 1 #guild biomass plots
rundietplots <- 1 #diet plots showing diet composition across run
rundietcomparison <- 0 #diet comparison plots

```

Authenticate Google so we can write to Google sheets
```{r authenticate, include=FALSE}

#if getting a Error in `gs4_get_impl_()`:
#! Client error: (400) FAILED_PRECONDITION
#make sure you are reading a google docs and not an .xlsx file


# Authenticate manually
#will open window, should be logged in browser with same account used to access the Google sheet
googlesheets4::gs4_auth()

# Set authentication token to be stored in a folder called `.secrets`
options(gargle_oauth_cache = ".secrets")

# If successful, the previous step stores a token file.
# Check that a file has been created with:
list.files(".secrets/")

#Authenticate using token. If no browser opens, the authentication works.
googlesheets4::gs4_auth(cache = ".secrets", email = myemail)


```

Load Google sheet with calibration changes
```{r get googlesheet, include=FALSE}
#Calibration Google sheet id (from browser bar)
sheet.id = "1KskR_Jzs33C_1zhSNwAPNCOliM9q6ftD7DSywSYW568"

prm.modify <- googlesheets4::read_sheet(sheet.id, sheet = sheet.name)

```

## Modify PRM

Creates run directories based on Google sheet runs, and modifies the PRM file based on the Google sheet prm.modify

```{r read prm changes, include=FALSE}
lapply(runs.modify, modify_prm, sheet.id, sheet.name, base.dir, run.dir, prm.modify, prm.name)


```



Manage Atlantis runs, will run the specified directories pulled from column "run_name" in the Google sheet

```{r manage runs, include=FALSE}


manage_atlantis_runs(sh.file, runs.modify, prm.modify, run.dir, flagnoclusters)


```


Extract biomass, numbers, ResN, StrN, and Weight-at-age for each functional group by run output, variables will be saved in each output folder
```{r get outputs, include=FALSE}

#loads functional group file
data(fungrouplist)

get_output_data(prm.modify, runs.modify, run.dir, run.time, fungrouplist, this.output.nc, maxtimestep)


```

Plot calibration results by run, a combined pdf with plots for biomass, reserve N, structural N, numbers and weight-at-age will be saved in the output folder
```{r plot runs, include=FALSE}

if(runbaseplots == 1) plot_calibration_runs(fungrouplist, prm.modify, run.dir)

```

Plot biomass comparison plots for all runs
```{r compare biomass, include=FALSE}

if(runcomparebiomass == 1) compare_biomass(fungrouplist, prm.modify, run.dir, maxtimestep, runs.modify)

```

Plot biomass by guild
```{r plot guild, include=FALSE}

if(runguildbiomass == 1) plot_guild_biomass(fungrouplist, prm.modify, group_guilds)
```

Plot diets
```{r plot diets, include=FALSE}

if(rundietplots == 1) plot_Diets(fungrouplist, prm.modify, runs.modify, threshold, outdietfile, starttimediet, endtimediet, run.dir)

```

Plot diet comparison
```{r plot diet comparison, include=FALSE}

if(rundietcomparison == 1){
  library("rbgm")

  check_diets_init(prm.modify, run.dir, runs.modify, fungrouplist, atlantis.bgm, prm.name, init_file=this.nc)

} 

```
