---
title: "run_calibration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{run_calibration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r load options, include=}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(scipen = 999)

#use this if installing sf from CRAN returns an error
#remotes::install_github("r-spatial/sf")

#only packages that are needed as loaded, functions from other packages are called directly as dplyr::filter
# List of packages for session
.packages = c("parallel","doSNOW")
#install.packages(.packages, dependencies = TRUE)
# Load packages into session 
lapply(.packages, require, character.only=TRUE)


devtools::load_all()
#install needed dependencies
system("sudo chmod + ~/atlantiscalib/data-raw/ubuntulibraries.sh", wait = TRUE)
system("sudo sh ~/atlantiscalib/data-raw/ubuntulibraries.sh", wait = TRUE)

```

Check these entries before running, specifies runs, paths and plots to generate
Note all plots are saved in the /outputFolder
```{r set run, include=FALSE}

flagnoclusters = 0 #flag to run on multiple cores, 1 to run on all cores except one, 0 to run on all cores, can help access Rstudio while Atlantis runs are going

#Check before running
#Name of sheet used in Google sheet calibration log
sheet.name = "calibration_log_example"

#runs that will be modified, based on run_no in the spreadsheet
runs.modify <- 1:2

#specify email used to access the Google sheet
myemail <- "hmorzarialuna@gmail.com"#"myemail@gmail.com"

#directory with base run
#base.dir <- "/home/atlantis/psatlantismodel/Atlantis_mv1_base_2024_5yrs_V2"
#directory where to store runs
run.dir <- "/nfsdata/ampscalibration"
#name of biology prm
prm.name <- "AMPSbioparam_mv1_2024_V4.prm"
#name of functional group file
fungrouplist <- readr::read_csv("~/atlantiscalib/data-raw/PugetSoundAtlantisFunctionalGroups_2024.csv")
#name of guild group file
group_guilds <- readr::read_csv("~/atlantiscalib/data-raw/group_guilds.csv")


sh.file <- "amps_cal.sh" #name sh file

startyear <- 2011 #model start year
this.nc <- "AMPS_2024.nc"
this.output.nc <- "AMPS_OUT.nc" #name of output nc file


#options for diet plots
atlantis.bgm <- here::here("data-raw","PugetSound_89b_070116.bgm")
outdietfile <- "AMPS_OUTDietCheck.txt"
atlantis.run <- "PugetSound_run.prm"

#plots to run, if these flags are turned off, this RMD will only create run folders, run them and gather output
runbaseplots <- 1 #baseplots are Biomass, ResN, StrN, Numbers, Weight-at-age for individual runs
runcomparebiomass <- 1 #compare biomass plots
runguildbiomass <- 1 #guild biomass plots
rundietplots <- 1 #diet plots showing diet composition across run
rundietcomparison <- 0 #diet comparison plots
plotbhcurves  <- 1 #plot Beverton Holt curves

```

Authenticate Google so we can write to Google sheets
```{r authenticate, include=FALSE}

#if getting a Error in `gs4_get_impl_()`:
#! Client error: (400) FAILED_PRECONDITION
#make sure you are reading a google docs and not an .xlsx file


# Authenticate manually
#will open window, should be logged in browser with same account used to access the Google sheet
googlesheets4::gs4_auth()

# Set authentication token to be stored in a folder called `.secrets`
options(gargle_oauth_cache = ".secrets")

# If successful, the previous step stores a token file.
# Check that a file has been created with:
list.files(".secrets/")

#Authenticate using token. If no browser opens, the authentication works.
googlesheets4::gs4_auth(cache = ".secrets", email = myemail)


```

Load Google sheet with calibration changes
```{r get googlesheet, include=FALSE}
#Calibration Google sheet id (from browser bar)
sheet.id = "1KskR_Jzs33C_1zhSNwAPNCOliM9q6ftD7DSywSYW568"

prm.modify <- googlesheets4::read_sheet(sheet.id, sheet = sheet.name)

```

## Modify input files

Creates run directories based on Google sheet runs, modifies the biology PRM file and run file to update run time based on the Google sheet prm.modify

```{r read prm changes, include=FALSE}

lapply(runs.modify, modify_prm, sheet.id, sheet.name, run.dir, prm.modify, prm.name, atlantis.run)


```



Manage Atlantis runs, will run the specified directories pulled from column "run_name" in the Google sheet

```{r manage runs, include=FALSE}


manage_atlantis_runs(sh.file, runs.modify, prm.modify, run.dir, flagnoclusters)


```


Extract biomass, numbers, ResN, StrN, and Weight-at-age for each functional group by run output, variables will be saved in each output folder
```{r get outputs, include=FALSE}

#loads functional group file
data(fungrouplist)

get_output_data(prm.modify, runs.modify, run.dir, run.time, fungrouplist, this.output.nc)


```

Plot calibration results by run, a combined pdf with plots for biomass, reserve N, structural N, numbers and weight-at-age will be saved in the output folder
```{r plot runs, include=FALSE}

if(runbaseplots == 1) plot_calibration_runs(fungrouplist, prm.modify, run.dir)

```

Plot biomass comparison plots for all runs
```{r compare biomass, include=FALSE}

if(runcomparebiomass == 1) compare_biomass(fungrouplist, prm.modify, run.dir, runs.modify)

```

Plot biomass by guild
```{r plot guild, include=FALSE}

if(runguildbiomass == 1) plot_guild_biomass(fungrouplist, prm.modify, group_guilds)
```

Plot diets
```{r plot diets, include=FALSE}

#NOTE diet plots are saved in the /outputFolder of every run
if(rundietplots == 1) plot_diets(fungrouplist, prm.modify, runs.modify, outdietfile, run.dir)

```

Plot diet comparison
```{r plot diet comparison, include=FALSE}

if(rundietcomparison == 1){
  
  library("rbgm")
  check_diets_init(prm.modify, run.dir, runs.modify, fungrouplist, atlantis.bgm, prm.name, init_file=this.nc)

} 

```

```{r}

if(plotbhcurves ==1){

   bh_plot(this.nc, fg.table=fungrouplist, bio.prm = prm.name, prm.modify, runs.modify, run.dir)
}

```

